\plaintitle

### 2016-09-21 Paper/proceedings.tex
Submitted version.

%The average absolute error of slope estimation across all conditions had an interquartile mean of $0.06$ for slope values ranging from $\{-1,1\}$, corresponding to an error rate of $17\%$ of the actual slopes. 
Prior work in graphical perception often measures the absolute log error: e.g., Cleveland \& McGill~\cite{cleveland1984graphical} calculate their performance metric as ($log_2 |\text{error}| + \frac{1}{8}$). As a point of comparison the interquartile mean of the absolute log error, calculated as per  was $2.4$ across all conditions in this experiment. Differences in methodology and measurement discourage statistical inferences comparing this value with those in similar experiments. Nevertheless, error rates for regression by eye are at least in the same magnitude as those observed in other graphical perception tasks in both lab and crowdsourced studies. For instance, Heer \& Bostock~\cite{heer2010crowdsourcing} report an absolute log error of $2.5$ for proportional judgments in treemaps, and Cleveland \& McGill~\cite{cleveland1984graphical} report an absolute log error of $2.4$ for proportional judgments in stacked bars (although compare to a log error of estimation of relative lengths of lines of $1.1$). This similarity suggests that, despite requiring estimation of aggregate statistical information, regression by eye results in judgments that are accurate enough for many practical purposes, comparable with the expected accuracy in comparing individual values in visualizations.

>>>>

%The average absolute error of slope estimation across all conditions had an interquartile mean of $0.06$ for slope values ranging from $\{-1,1\}$, corresponding to an error rate of $17\%$ of the actual slopes. 
Prior work in graphical perception often measures performance as the absolute log error: e.g., Cleveland \& McGill~\cite{cleveland1984graphical} calculate their performance metric as $\log_2 (|\text{error}| + \frac{1}{8}$). As a point of comparison, the interquartile mean of the absolute log error across all conditions in this experiment was $2.4$. Differences in methodology and measurement discourage statistical inferences comparing this value with those in similar experiments. Nevertheless, error rates for regression by eye are at least in the same magnitude as those observed in other graphical perception tasks in both lab and crowdsourced studies. For instance, Heer \& Bostock~\cite{heer2010crowdsourcing} report an absolute log error of $2.5$ for proportional judgments in treemaps, and Cleveland \& McGill~\cite{cleveland1984graphical} report an absolute log error of $2.4$ for proportional judgments in stacked bars (although compare to a log error of estimation of relative lengths of lines of $1.1$). This similarity suggests that, despite requiring estimation of aggregate statistical information, regression by eye results in judgments that are accurate enough for many practical purposes, comparable with the expected accuracy in comparing individual values in visualizations.
